Proportional multi-state multiple-cohort life table model

### 2018-04-03 MSLT/MSLTdoc.Rmd
Start code explanation

#Packages to run code
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
options(knitr.table.format = 'latex')
```
# Introduction

@@

>>>>

#The work in this document requires the following packages (code, rmarkdown and citing packages):
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
options(knitr.table.format = 'latex')
```
# Introduction

@@

##Code
